Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-05-08 automatica/paper.tex
changed affiliation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\author[oxford]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
\author[manaus]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
\author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
\author[oxford,manaus]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
\author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
\author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}

\address[oxford]{University of Oxford, UK}
\address[cambridge]{University of Cambridge, UK}
\address[manaus]{Federal University of Amazonas, Brazil}

\begin{keyword}                           % Five to ten keywords,  
Digital control synthesis; Safety requirements; A/D converters; Quantization errors; Sampling.               % chosen from the IFAC 
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

Modern implementations of embedded control systems have proliferated
with the availability of low-cost devices that can perform highly
non-trivial control tasks, with significant impact in numerous
application areas such as life sciences, environmental control and
robotics~\cite{astrom1997computer, Franklin15}.  Correct synthesis of
control software for such platforms is non-trivial, even in cases with
restricted dynamics.

In this paper, we examine the case of Linear Time Invariant (LTI)
models, for which the synthesis of controllers is well understood.
However, the use of digital control architectures adds new challenges
caused by artifacts specific to digital control, such as the effects
of finite-precision arithmetic, time discretization and quantization
noise introduced by A/D and D/A conversion.
%
Given an LTI model, we develop an automatic technique for generating
correct-by-construction digital controllers that addresses all these
challenges. Specifically, we synthesize stable and safe,
software-implemented embedded controllers.  Due to the complexity of
such closed-loop systems, we focus on linear models with known
configurations, and perform parametric synthesis of controllers.
%meeting a number of properties that define their desired behavior.

@@

Our work addresses challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model,
where the plant exhibits continuous behavior whereas the controller
operates in discrete time and over a quantized domain.  In particular,
our model evaluates the effects of the quantizers (A/D and D/A
converters) and of time discretization, as well as representation
errors introduced by modeling %% artifacts such as an
%% observer~\cite{astrom1997computer}
in a finite precision domain, while reasoning about high level
properties such as stability, robustness, and safety, which define the
behaviour of the system.  Notably, safety requirements are
frequently overlooked in conventional feedback control synthesis, but
play an important role in systems engineering.

>>>>

\author[oxford]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
\author[manaus]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
\author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
\author[manchester]{Lucas Cordeiro}\ead{lucas.cordeiro@manchester.ac.uk},
\author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
\author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}

\address[oxford]{University of Oxford, UK}
\address[cambridge]{University of Cambridge, UK}
\address[manchester]{University of Manchester, UK}
\address[manaus]{Federal University of Amazonas, Brazil}

\begin{keyword}                           % Five to ten keywords,  
Digital control synthesis; Safety requirements; Analog/Digital conversion; Quantization errors; Sampling.               % chosen from the IFAC 
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

Modern implementations of embedded control systems have proliferated
with the availability of low-cost devices that can perform highly
non-trivial control tasks, with significant impact in numerous
application areas such as the life sciences, high-precision control, 
automotive and robotics~\cite{astrom1997computer, Franklin15}.  
Provably correct synthesis of control software for such platforms is non-trivial, 
even in cases with unsophisticated dynamics.

In this paper, we examine the case of Linear Time Invariant (LTI)
models, for which the synthesis of controllers is well understood.
However, the use of digital control architectures adds new challenges
caused by artefacts specific to digital control, such as the effects
of finite-precision arithmetic, time discretization and quantization
noise introduced by A/D and D/A conversion.
%
Given an LTI model, we develop an automatic technique for generating
correct-by-construction digital controllers that addresses all these
challenges. Specifically, we automatically synthesize stable and safe,
software-implemented embedded controllers.  
%Due to the complexity of
%such closed-loop systems, we focus on linear models with known
%configurations, and perform parametric synthesis of controllers.
%meeting a number of properties that define their desired behavior.

@@

Our work addresses challenging aspects of the control synthesis problem:  
we perform digital control synthesis over a ``hybrid model'',
namely a model encompassing a plant exhibiting continuous behavior, 
whereas the controller operates in discrete time and over a quantized domain.  
In particular, our model evaluates the effects of the quantizers (A/D and D/A
converters) and of time discretization, as well as representation
errors introduced by working  %% artifacts such as an
%% observer~\cite{astrom1997computer}
in a finite-precision domain. 
We reason about high level properties such as stability, robustness, and safety, which define the
behaviour of the whole model.  
Notably, safety requirements are frequently overlooked in conventional feedback control synthesis, but
play a key role in systems engineering, particularly in safety-critical applications.
